Type Error Telemetry at Scale: Pseudonymized and Stochiastic

### 2023-09-17 programming23/paper.tex
codebase size

Roblox Studio collected type error telemetry in Spring 2023,
between February and April.
Every Studio session had a small random chance of generating
telemetry~(\cref{s:telemetry-records}).
The chosen sessions generated a record whenever the user switched modules and
randomly on each keystroke.

\Cref{f:records-per-hour} provides a time-ordered distribution of the data.
Each vertical bar counts the number of records generated per hour according to
a client-side timestamp.
The bars are labeled with a California time zone because that is the locale of
the Roblox servers, which parsed the timestamps.
Most buckets contain roughly one thousand records, but some have very few
and a handful of others exceed three thousand.
%% \FILL{} investigate one tower, what's happening?? all one session?
There is a sharp drop in early April because we disabled telemetry at that point
but some clients continued to generate data
(\FILL{} Q. Alan, is that an ok sentence? I'm not sure why there's a long tail,
guess it could be people not updating studio or people with strange time settings
on their machine.)
We do not know which timezone the records originated in, but since the counts
tend to peak midday California time it seems that the majority
of Roblox developers are following a Western Hemisphere schedule.
%% \FILL{} probably North America, but do we really want to guess?
The counts for weekends (shaded regions) are often the tallest; these days presumably
have a larger number of sessions for telemetry to observe.

@@

\begin{figure}[t]
  % ;; (list* (max* vv) (median < vv) mm (stddev/mean mm vv) (percentile* vv)))
  % ;; percentile* = 0.95 -- 0.99
  %#hash((editrange . (1156036 926 3007043/817 30975.40553032358 (0.95 8220) (0.96 9858) (0.97 13656) (0.98 18956) (0.99 34725)))
  %      (event-count . (6079 138 38689/135 582.5752201972966 (0.95 960) (0.96 1174) (0.97 1304) (0.98 1836) (0.99 3302)))
  %      (files . (54884 7678 55257996/4639 11853.650098459446 (0.95 40029) (0.96 42771) (0.97 45417) (0.98 48688) (0.99 51761)))
  %      (lines . (1089963 3115 38928947/5992 22364.75846303099 (0.95 18561) (0.96 25892) (0.97 27014) (0.98 29725) (0.99 50547)))
  %      (timespan . (1387897376 845648 591343604248/185705 15724745.722577972 (0.95 10696064) (0.96 12715468) (0.97 15596940) (0.98 21153924) (0.99 35450460))))
  %% NOTE: 3 records have +1M lines, all from one nocheck session, all with 3 files
  %% - session "30,762,216,447,324"
  %% NOTE: 133 records have +52K files, all from one nocheck session
  %% - session "330,172,870,224,081" 
  %% (2nd biggest has 41K files "31,650,473,913,529")

  \begin{tabular}{l@{}r@{~}l@{}r@{~}l@{}r@{~}l}
                 & Files  &              &     Lines &             &    Edit Range & \\
    Mean [std]   & 11,911 & \stddev{31}  &     6,497 & \stddev{22} &         3,680 & \stddev{12} \\
    Median       &  7,678 &              &     3,115 &             &           926 & \\
    \pct{99}     & 51,761 &              &    50,547 &             &        34,725 & \\
    & \includegraphics[width=0.2\columnwidth]{img/files-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/lines-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/editrange-distribution.pdf}

@@

TODO findings lessons etc.

FILL power-law files lines editrange.
Incredible max numbers.

\subsection{??? records}

@@

\Cref{f:dataset-overview}

>>>>

Roblox Studio collected type error telemetry in Spring 2023,
between February and April.
Every Studio session had a small random chance of generating
telemetry~(\cref{s:telemetry-records}).
The chosen sessions generated a record whenever the user switched modules and
randomly on each keystroke.
In total we collected 1.5 million telemetry records.

\Cref{f:records-per-hour} provides a time-ordered distribution of the data.
Each vertical bar counts the number of records generated per hour according to
a client-side timestamp.
The bars are labeled with a California time zone because that is the locale of
the Roblox servers, which parsed the timestamps.
Most buckets contain roughly one thousand records, but some have very few
and a handful of others exceed three thousand.
%% \FILL{} investigate one tower, what's happening?? all one session?
There is a sharp drop in early April because we disabled telemetry at that point
but some clients continued to generate data
(\FILL{} Q. Alan, is that an ok sentence? I'm not sure why there's a long tail,
guess it could be people not updating studio or people with strange time settings
on their machine.)
We do not know which timezone the records originated in, but since the counts
tend to peak midday California time it seems that the majority
of Roblox developers are following a USA schedule (or rather, a Western
Hemisphere schedule).
The counts for weekends (shaded regions) are often the tallest; these days presumably
have a larger number of sessions for telemetry to observe.

@@

\begin{figure}[t]
  % ;; (list* (max* vv) (median < vv) mm (stddev/mean mm vv) (percentile* vv)))
  % ;; percentile* = 0.95 -- 0.99
  % #hash((editrange . (1156036 926 3007043/817 30975.40553032358 (0.95 8220) (0.96 9858) (0.97 13656) (0.98 18956) (0.99 34725)))
  %       (event-count . (6079 138 38689/135 582.5752201972966 (0.95 960) (0.96 1174) (0.97 1304) (0.98 1836) (0.99 3302)))
  %       (files . (54884 7678 55257996/4639 11853.650098459446 (0.95 40029) (0.96 42771) (0.97 45417) (0.98 48688) (0.99 51761)))
  %       (lines . (1089963 3115 38928947/5992 22364.75846303099 (0.95 18561) (0.96 25892) (0.97 27014) (0.98 29725) (0.99 50547)))
  %       (timespan . (1387897376 845648 591343604248/185705 15724745.722577972 (0.95 10696064) (0.96 12715468) (0.97 15596940) (0.98 21153924) (0.99 35450460))))
  %% NOTE: 3 records have +1M lines, all from one nocheck session, all with 3 files
  %% - session "30,762,216,447,324"
  %% NOTE: 133 records have +52K files, all from one nocheck session
  %% - session "330,172,870,224,081" 
  %% (2nd biggest has 41K files "31,650,473,913,529")

  \begin{tabular}{l@{}r@{~}l@{}r@{~}l@{}r@{~}l}
                 & Files  &              &     Lines &             &    Edit Range & \\
    Mean [std]   & 11,911 & \stddev{12}  &     6,497 & \stddev{22} &         3,680 & \stddev{31} \\
    Median       &  7,678 &              &     3,115 &             &           926 & \\
    \pct{99}     & 51,761 &              &    50,547 &             &        34,725 & \\
    & \includegraphics[width=0.2\columnwidth]{img/files-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/lines-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/editrange-distribution.pdf}

@@

\Cref{f:codebase-size} summarizes the size of projects in the dataset.
The top half of the figure reports the mean, standard deviation, median,
and {99}th percentile for the number of files, lines, and lines in edit range.
The bottom half shows zoomed-in distributions of the file, line, and edit range
numbers.
For example, the x-axis of the first plot ranges from 0 to 1,000 files and
the y-axis counts up to 1,000 telemetry records.

There is a huge amount of variation across projects.
The largest ones have over 50k files (!) and 50k lines of code, and
there are many small ones with 1 file and/or 1 line of code.
Unsurprisingly, the numbers come with large standard deviations.
The median values are more reasonable, with roughly 3,000 lines of code
and 1,000 lines in edit ranges, but still have a large number of files: over 7,000.
The high number of files may be because creators define mavy components to
build a Roblox experience and put these components in separate files.
(\FILL{} still that's a lot of components ... any better guesses+)

\subsection{Type Analysis Modes}

@@

\Cref{f:dataset-overview} breaks down the dataset ...
